Perturbing SU($n$)-symmetric interactions

### 2020-01-30 collective_sun/sun_perturbation.tex
fix mistake in last derivation

In order to write out the factors in \eqref{eq:sym_prod_group_start}
explicitly, we define
\begin{align}
  \abs{g} \equiv \sum_{S\in\PP\p{\ZZ_p}} g_S,
\end{align}
which is equivalent to the total number of dots in the Venn diagram
associated with $g$, and identify the set of values that the distinct
indices assigned according to $g$ can take:
\begin{align}
  \C_N\p{g}
  \equiv \set{ k \in \bigotimes_{S\in\PP\p{\ZZ_p}} \C_N\p{g_S}
    : \t{all elements of $k$ are distinct} }
  \simeq \C_N\p{\abs{g}},
\end{align}
where each $k\in\C_N\p{g}$ has the natural decomposition
$k=\p{k_S:S\in\PP\p{\ZZ_p}}$ with $k_S\in\C_N\p{g_S}$.  We then define
the restriction of $k\in\C_N\p{g}$ to values associated with $w_j$ and
$O_j$:
\begin{align}
  k_j \equiv \bigcup_{S\in\PP\p{\ZZ_p} : j\in S} k_S
  = \bigcup_{R\in\PP\p{\ZZ_p\setminus\set{j}}} k_{\set{j}\cup R},
\end{align}
where the union of lists $k_S$ denotes a concatenation of those lists.
We then have that
\begin{align}
  w\p{g} \equiv \sum_{k\in\C_N\p{g}} \prod_{j\in\ZZ_p} w_j\p{k_j},
  &&
  O\p{g} \equiv \prod_{j\in\ZZ_p}
  O_j\p{\ell_j}~\t{for some}~\ell\in\C_N\p{g},
\end{align}
where the choice of $\ell\in\C_N\p{g}$ does not matter after
projection onto fully symmetric manifold, and
\begin{align}
  \S\p{g} \equiv \sp{\prod_{j\in\ZZ_p} { M_j \choose g_S : j\in S }}
  \sp{\prod_{S\in\PP\p{\ZZ_p}} \p{g_S!}^\abs{S}}
  = \prod_{j\in\ZZ_p} M_j!,
  \label{eq:sym_prod_symmetry}
\end{align}
where the first product in \eqref{eq:sym_prod_symmetry} contains
multinomial coefficients
\begin{align}
  { M \choose a_1, a_2, \cdots, a_m }
  \equiv \f{M!}{a_1!a_2!\cdots a_m!},
\end{align}
that account for the number of ways to partition the indices of each
$w_j,O_j$ into sets of shared indices according to $g_S$ for all
$j\in S$, and the second product in \eqref{eq:sym_prod_symmetry}
accounts for the number of ways to permute each set of shared indices
on every tensor.  Altogether, the symmetry factors $\S\p{g}$ turn out
to be independent of $g$, and cancel out exactly with the $\sim M_j!$
prefactors in \eqref{eq:sym_prod_vec}, so
\begin{align}
  \prod_{j\in\ZZ_p} \sum_{k\in\C_N\p{M_j}} w_j\p{k} O_j\p{k}
  \EQFS \sum_{g\in\G\p{\m M}} w\p{g} O\p{g}.
  \label{eq:sym_prod_group}
\end{align}

>>>>

In order to write out the factors in \eqref{eq:sym_prod_group_start}
explicitly, we identify the set of values that the distinct indices
assigned according to $g$ can take:
\begin{align}
  \C_N\p{g}
  \equiv \set{ k \in \bigotimes_{S\in\PP\p{\ZZ_p}} \C_N\p{g_S}
    : \t{all elements of $k$ are distinct} },
\end{align}
where each $k\in\C_N\p{g}$ has the natural decomposition
$k=\p{k_S:S\in\PP\p{\ZZ_p}}$ with $k_S\in\C_N\p{g_S}$.  We then define
the restriction of $k\in\C_N\p{g}$ to values associated with $w_j$ and
$O_j$:
\begin{align}
  k_j \equiv \bigcup_{S\in\PP\p{\ZZ_p} : j\in S} k_S
  = \bigcup_{R\in\PP\p{\ZZ_p\setminus\set{j}}} k_{\set{j}\cup R},
\end{align}
where the union of lists $k_S$ denotes a concatenation of those lists.
These definitions allow us to expand
\begin{align}
  w\p{g} \equiv \sum_{k\in\C_N\p{g}} \prod_{j\in\ZZ_p} w_j\p{k_j},
  &&
  O\p{g} \equiv \prod_{j\in\ZZ_p}
  O_j\p{\ell_j}~\t{for some}~\ell\in\C_N\p{g},
\end{align}
where the choice of $\ell\in\C_N\p{g}$ does not matter after
projection onto fully symmetric manifold, and
\begin{align}
  \S\p{g} \equiv \sp{\prod_{j\in\ZZ_p} { M_j \choose g_S : j\in S }}
  \sp{\prod_{S\in\PP\p{\ZZ_p}} \p{g_S!}^\abs{S}}
  = \prod_{j\in\ZZ_p} M_j!,
  \label{eq:sym_prod_symmetry}
\end{align}
where the first product in \eqref{eq:sym_prod_symmetry} contains
multinomial coefficients
\begin{align}
  { M \choose a_1, a_2, \cdots, a_m }
  \equiv \f{M!}{a_1!a_2!\cdots a_m!},
\end{align}
that account for the number of ways to partition the indices of each
$w_j,O_j$ into sets of shared indices according to $g_S$ for all
$j\in S$, and the second product in \eqref{eq:sym_prod_symmetry}
accounts for the number of ways to permute each set of shared indices
on every tensor.  Altogether, the symmetry factors $\S\p{g}$ cancel
out with the $\sim M_j!$ prefactors in \eqref{eq:sym_prod_vec}, so
\begin{align}
  \prod_{j\in\ZZ_p} \sum_{k\in\C_N\p{M_j}} w_j\p{k} O_j\p{k}
  \EQFS \sum_{g\in\G\p{\m M}} w\p{g} O\p{g}.
  \label{eq:sym_prod_group}
\end{align}
